\documentclass[12pt]{article}

\title{ODEs and Multivariate functions}
\author{
	Evan M Drake \\
	\texttt{drakeev@butte.edu}
}


\usepackage{snow-preamble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	\maketitle
	\tableofcontents

	\newpage

	%% body start

	\section{ODEs}
		Differential Equations (DE)\footnote{
			see \url{https://en.wikipedia.org/wiki/Ordinary_differential_equation}
			}allow us to track $\frac{\Delta}{\text{time}}$ that is to say the change over time of some system.
		The exact nature of that system is dependent on what makes the system up.
		An \textit{Ordinary} DE is based around a single differentiator,
			in particular there is only a single independent variable on which we differentiate.
		It is the case that there is more complexity to this field that comes in the form of differentiation depth,
			functions involved in the equation,
			etc.
		It is the case that many of my students will be in differential equations at the time of this course,
			such that an improper or quick overview will not be proper.
		That is for this section we will learn what MATLAB uses diffs for and how we can solve them.
		In particular what it means to solve them.
		\textbf{That I know of} there is no universal goal of solving a DE other than to reduce it to some understandable series.

	\section{Program Organization}
		This topic is out of scope for engineers,
			thus I will give the briefest of overviews on this field.
		You organize a program the same way you organize your thoughts on a problem.
		In particular you think of a program as a problem to be solved or a theorem to be proved.
		A program has inputs and outputs such that given its necessary inputs it should always give you the desired output.
		There is a multitude of ways to do this we discuss in lecture.

	\section{Logical Vectors}
		A logical vector is special to MATLAB such that I have not seen it else where in the computer science literature.
		A logical vector is a vector of boolean values,
			why this could be useful we will discuss in the lecture.

	%% body finish

	\nocite{*}

	\newpage % bib
	\backmatter
	\addcontentsline{toc}{section}{References}
	\printbibliography

	\newpage % index
	\printindex

	\newpage % appendices
	\appendix

\end{document}

