\documentclass[12pt]{article}

\title{Paper on approximal algorithms}
\author{
	Evan M Drake \\
	\texttt{}
}


\usepackage{snow-preamble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

	\maketitle

	%% body start

	The goal of this paper is to make yourself familiar with an approximation algorithms.
	There is a multitude of uses for these algorithms but I would like a theoretical examination of them.
	This assignment will happen in three stages:
	\begin{enumerate}
		\item find an area of interest
		\item explore that area and choose an approximation algorithm
		\item write a paper about that algorithm (several drafts would be good)
	\end{enumerate}
	It is the case that for this assignment there should exist certain things in your paper.
	In particular you should address:
		What area of mathematics your algorithm is from;
		The original creator of the algorithm;
		Why your algorithm is interesting in comparison with the other possible options (if any exist).
	
	Again there will be no rubric for this as all the papers will find \textit{interesting} to mean different things.
	You should follow a writing standard of some kind the following are all acceptable options: AMS, IEEE, APA.
	You can omit the abstract, section titles, appendices, and index from the standard of your choice.
	Please pay attention to your references section,
		in particular make sure to cite any material you find even if you do not quote it directly.
	Above all else a paper should be fun to write so go explore this more mathy assignment to the best of your ability.

	%% body finish

	\nocite{*}

	\newpage % bib
	\backmatter

\end{document}

